\startmanpage
\mantitle{MPI{\tt \char`\_}Reduce{\tt \char`\_}scatter}{tex}{10/24/2006}
\manname{MPI{\tt \char`\_}Reduce{\tt \char`\_}scatter}
--- Combines values and scatters the results 
\subhead{Synopsis}
\startvb\begin{verbatim}
int MPI_Reduce_scatter(void *sendbuf, void *recvbuf, int *recvcnts, 
                      MPI_Datatype datatype, MPI_Op op, MPI_Comm comm)

\end{verbatim}
\endvb

\subhead{Input Parameters}
\startarg{sendbuf }{starting address of send buffer (choice) 
}
\startarg{recvcounts }{integer array specifying the 
number of elements in result distributed to each process.
Array must be identical on all calling processes. 
}
\startarg{datatype }{data type of elements of input buffer (handle) 
}
\startarg{op }{operation (handle) 
}
\startarg{comm }{communicator (handle) 
}
\par
\subhead{Output Parameter}
\startarg{recvbuf }{starting address of receive buffer (choice) 
}
\par
\subhead{Thread and Interrupt Safety}
\par
This routine is thread-safe.  This means that this routine may be
safely used by multiple threads without the need for any user-provided
thread locks.  However, the routine is not interrupt safe.  Typically,
this is due to the use of memory allocation routines such as {\tt malloc
}or other non-MPICH runtime routines that are themselves not interrupt-safe.
\par
\subhead{Notes for Fortran}
All MPI routines in Fortran (except for {\tt MPI{\tt \char`\_}WTIME} and {\tt MPI{\tt \char`\_}WTICK}) have
an additional argument {\tt ierr} at the end of the argument list.  {\tt ierr
}is an integer and has the same meaning as the return value of the routine
in C.  In Fortran, MPI routines are subroutines, and are invoked with the
{\tt call} statement.
\par
All MPI objects (e.g., {\tt MPI{\tt \char`\_}Datatype}, {\tt MPI{\tt \char`\_}Comm}) are of type {\tt INTEGER
}in Fortran.
\par
\subhead{Notes on collective operations}
\par
The reduction functions ({\tt MPI{\tt \char`\_}Op}) do not return an error value.  As a result,
if the functions detect an error, all they can do is either call {\tt MPI{\tt \char`\_}Abort
}or silently skip the problem.  Thus, if you change the error handler from
{\tt MPI{\tt \char`\_}ERRORS{\tt \char`\_}ARE{\tt \char`\_}FATAL} to something else, for example, {\tt MPI{\tt \char`\_}ERRORS{\tt \char`\_}RETURN},
then no error may be indicated.
\par
The reason for this is the performance problems in ensuring that
all collective routines return the same error value.
\par
\subhead{Errors}
\par
All MPI routines (except {\tt MPI{\tt \char`\_}Wtime} and {\tt MPI{\tt \char`\_}Wtick}) return an error value;
C routines as the value of the function and Fortran routines in the last
argument.  Before the value is returned, the current MPI error handler is
called.  By default, this error handler aborts the MPI job.  The error handler
may be changed with {\tt MPI{\tt \char`\_}Comm{\tt \char`\_}set{\tt \char`\_}errhandler} (for communicators),
{\tt MPI{\tt \char`\_}File{\tt \char`\_}set{\tt \char`\_}errhandler} (for files), and {\tt MPI{\tt \char`\_}Win{\tt \char`\_}set{\tt \char`\_}errhandler} (for
RMA windows).  The MPI-1 routine {\tt MPI{\tt \char`\_}Errhandler{\tt \char`\_}set} may be used but
its use is deprecated.  The predefined error handler
{\tt MPI{\tt \char`\_}ERRORS{\tt \char`\_}RETURN} may be used to cause error values to be returned.
Note that MPI does {\em not} guarentee that an MPI program can continue past
an error; however, MPI implementations will attempt to continue whenever
possible.
\par
\startarg{MPI{\tt \char`\_}SUCCESS }{No error; MPI routine completed successfully.
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}COMM }{Invalid communicator.  A common error is to use a null
communicator in a call (not even allowed in {\tt MPI{\tt \char`\_}Comm{\tt \char`\_}rank}).
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}COUNT }{Invalid count argument.  Count arguments must be 
non-negative; a count of zero is often valid.
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}TYPE }{Invalid datatype argument.  May be an uncommitted 
MPI{\tt \char`\_}Datatype (see {\tt MPI{\tt \char`\_}Type{\tt \char`\_}commit}).
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}BUFFER }{Invalid buffer pointer.  Usually a null buffer where
one is not valid.
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}OP }{Invalid operation.  MPI operations (objects of type {\tt MPI{\tt \char`\_}Op})
must either be one of the predefined operations (e.g., {\tt MPI{\tt \char`\_}SUM}) or
created with {\tt MPI{\tt \char`\_}Op{\tt \char`\_}create}.
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}BUFFER }{This error class is associcated with an error code that
indicates that two buffer arguments are {\em aliased}; that is, the 
describe overlapping storage (often the exact same storage).  This
is prohibited in MPI (because it is prohibited by the Fortran 
standard, and rather than have a separate case for C and Fortran, the
MPI Forum adopted the more restrictive requirements of Fortran).
}
\location{red{\tt \char`\_}scat.c}
\endmanpage
