\startmanpage
\mantitle{MPI{\tt \char`\_}Type{\tt \char`\_}indexed}{tex}{5/8/2006}
\manname{MPI{\tt \char`\_}Type{\tt \char`\_}indexed}
--- Creates an indexed datatype 
\subhead{Synopsis}
\startvb\begin{verbatim}
int MPI_Type_indexed(int count,
                    int blocklens[],
                    int indices[],
                    MPI_Datatype old_type,
                    MPI_Datatype *newtype)

\end{verbatim}
\endvb

\subhead{Input Parameters}
\startarg{count }{number of blocks -- also number of entries in indices and blocklens
}
\startarg{blocklens }{number of elements in each block (array of nonnegative integers) 
}
\startarg{indices }{displacement of each block in multiples of old{\tt \char`\_}type (array of 
integers)
}
\startarg{old{\tt \char`\_}type }{old datatype (handle) 
}
\par
\subhead{Output Parameter}
\startarg{newtype }{new datatype (handle) 
}
\par
\subhead{Thread and Interrupt Safety}
\par
This routine is thread-safe.  This means that this routine may be
safely used by multiple threads without the need for any user-provided
thread locks.  However, the routine is not interrupt safe.  Typically,
this is due to the use of memory allocation routines such as {\tt malloc
}or other non-MPICH runtime routines that are themselves not interrupt-safe.
\par
\subhead{Notes for Fortran}
All MPI routines in Fortran (except for {\tt MPI{\tt \char`\_}WTIME} and {\tt MPI{\tt \char`\_}WTICK}) have
an additional argument {\tt ierr} at the end of the argument list.  {\tt ierr
}is an integer and has the same meaning as the return value of the routine
in C.  In Fortran, MPI routines are subroutines, and are invoked with the
{\tt call} statement.
\par
All MPI objects (e.g., {\tt MPI{\tt \char`\_}Datatype}, {\tt MPI{\tt \char`\_}Comm}) are of type {\tt INTEGER
}in Fortran.
\par
The indices are displacements, and are based on a zero origin.  A common error
is to do something like to following
\begin{verbatim}
    integer a(100)
    integer blens(10), indices(10)
    do i=1,10
         blens(i)   = 1
10       indices(i) = 1 + (i-1)*10
    call MPI_TYPE_INDEXED(10,blens,indices,MPI_INTEGER,newtype,ierr)
    call MPI_TYPE_COMMIT(newtype,ierr)
    call MPI_SEND(a,1,newtype,...)
\end{verbatim}

expecting this to send {\tt a(1),a(11),...} because the indices have values
{\tt 1,11,...}.   Because these are {\em displacements} from the beginning of {\tt a},
it actually sends {\tt a(1+1),a(1+11),...}.
\par
If you wish to consider the displacements as indices into a Fortran array,
consider declaring the Fortran array with a zero origin
\begin{verbatim}
    integer a(0:99)
\end{verbatim}

\par
\subhead{Errors}
\par
All MPI routines (except {\tt MPI{\tt \char`\_}Wtime} and {\tt MPI{\tt \char`\_}Wtick}) return an error value;
C routines as the value of the function and Fortran routines in the last
argument.  Before the value is returned, the current MPI error handler is
called.  By default, this error handler aborts the MPI job.  The error handler
may be changed with {\tt MPI{\tt \char`\_}Comm{\tt \char`\_}set{\tt \char`\_}errhandler} (for communicators),
{\tt MPI{\tt \char`\_}File{\tt \char`\_}set{\tt \char`\_}errhandler} (for files), and {\tt MPI{\tt \char`\_}Win{\tt \char`\_}set{\tt \char`\_}errhandler} (for
RMA windows).  The MPI-1 routine {\tt MPI{\tt \char`\_}Errhandler{\tt \char`\_}set} may be used but
its use is deprecated.  The predefined error handler
{\tt MPI{\tt \char`\_}ERRORS{\tt \char`\_}RETURN} may be used to cause error values to be returned.
Note that MPI does {\em not} guarentee that an MPI program can continue past
an error; however, MPI implementations will attempt to continue whenever
possible.
\par
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}COUNT }{Invalid count argument.  Count arguments must be 
non-negative; a count of zero is often valid.
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}TYPE }{Invalid datatype argument.  May be an uncommitted 
MPI{\tt \char`\_}Datatype (see {\tt MPI{\tt \char`\_}Type{\tt \char`\_}commit}).
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}ARG }{Invalid argument.  Some argument is invalid and is not
identified by a specific error class (e.g., {\tt MPI{\tt \char`\_}ERR{\tt \char`\_}RANK}).
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}INTERN }{This error is returned when some part of the MPICH 
implementation is unable to acquire memory.  
}
\location{type{\tt \char`\_}indexed.c}
\endmanpage
