\startmanpage
\mantitle{MPI{\tt \char`\_}Errhandler{\tt \char`\_}create}{tex}{5/8/2006}
\manname{MPI{\tt \char`\_}Errhandler{\tt \char`\_}create}
--- Creates an MPI-style errorhandler 
\subhead{Synopsis}
\startvb\begin{verbatim}
int MPI_Errhandler_create(MPI_Handler_function *function, 
                          MPI_Errhandler *errhandler)

\end{verbatim}
\endvb

\subhead{Input Parameter}
\startarg{function }{user defined error handling procedure 
}
\par
\subhead{Output Parameter}
\startarg{errhandler }{MPI error handler (handle) 
}
\par
\subhead{Notes}
The MPI Standard states that an implementation may make the output value
(errhandler) simply the address of the function.  However, the action of
{\tt MPI{\tt \char`\_}Errhandler{\tt \char`\_}free} makes this impossible, since it is required to set the
value of the argument to {\tt MPI{\tt \char`\_}ERRHANDLER{\tt \char`\_}NULL}.  In addition, the actual
error handler must remain until all communicators that use it are
freed.
\par
\subhead{Thread and Interrupt Safety}
\par
This routine is thread-safe.  This means that this routine may be
safely used by multiple threads without the need for any user-provided
thread locks.  However, the routine is not interrupt safe.  Typically,
this is due to the use of memory allocation routines such as {\tt malloc
}or other non-MPICH runtime routines that are themselves not interrupt-safe.
\par
\subhead{Deprecated Function}
The MPI-2 standard deprecated a number of routines because MPI-2 provides
better versions.  This routine is one of those that was deprecated.  The
routine may continue to be used, but new code should use the replacement
routine.
The replacement routine for this function is {\tt MPI{\tt \char`\_}Comm{\tt \char`\_}create{\tt \char`\_}errhandler}.
\par
\subhead{Notes for Fortran}
All MPI routines in Fortran (except for {\tt MPI{\tt \char`\_}WTIME} and {\tt MPI{\tt \char`\_}WTICK}) have
an additional argument {\tt ierr} at the end of the argument list.  {\tt ierr
}is an integer and has the same meaning as the return value of the routine
in C.  In Fortran, MPI routines are subroutines, and are invoked with the
{\tt call} statement.
\par
All MPI objects (e.g., {\tt MPI{\tt \char`\_}Datatype}, {\tt MPI{\tt \char`\_}Comm}) are of type {\tt INTEGER
}in Fortran.
\par
\subhead{Errors}
\par
All MPI routines (except {\tt MPI{\tt \char`\_}Wtime} and {\tt MPI{\tt \char`\_}Wtick}) return an error value;
C routines as the value of the function and Fortran routines in the last
argument.  Before the value is returned, the current MPI error handler is
called.  By default, this error handler aborts the MPI job.  The error handler
may be changed with {\tt MPI{\tt \char`\_}Comm{\tt \char`\_}set{\tt \char`\_}errhandler} (for communicators),
{\tt MPI{\tt \char`\_}File{\tt \char`\_}set{\tt \char`\_}errhandler} (for files), and {\tt MPI{\tt \char`\_}Win{\tt \char`\_}set{\tt \char`\_}errhandler} (for
RMA windows).  The MPI-1 routine {\tt MPI{\tt \char`\_}Errhandler{\tt \char`\_}set} may be used but
its use is deprecated.  The predefined error handler
{\tt MPI{\tt \char`\_}ERRORS{\tt \char`\_}RETURN} may be used to cause error values to be returned.
Note that MPI does {\em not} guarentee that an MPI program can continue past
an error; however, MPI implementations will attempt to continue whenever
possible.
\par
\startarg{MPI{\tt \char`\_}SUCCESS }{No error; MPI routine completed successfully.
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}INTERN }{This error is returned when some part of the MPICH 
implementation is unable to acquire memory.  
}
\par
\subhead{See Also}
 MPI{\tt \char`\_}Comm{\tt \char`\_}create{\tt \char`\_}errhandler, MPI{\tt \char`\_}Errhandler{\tt \char`\_}free
\nextline
\location{errhandler{\tt \char`\_}create.c}
\endmanpage
