\startmanpage
\mantitle{MPI{\tt \char`\_}Pack}{tex}{10/17/2006}
\manname{MPI{\tt \char`\_}Pack}
--- Packs a datatype into contiguous memory 
\subhead{Synopsis}
\startvb\begin{verbatim}
int MPI_Pack(void *inbuf,
             int incount,
             MPI_Datatype datatype,
             void *outbuf, 
             int outcount,
             int *position,
             MPI_Comm comm)

\end{verbatim}
\endvb

\subhead{Arguments}
\startarg{void *inbuf }{input buffer
}
\startarg{int incount }{input count
}
\startarg{MPI{\tt \char`\_}Datatype datatype }{datatype
}
\startarg{void *outbuf }{output buffer
}
\startarg{int outcount }{output count
}
\startarg{int *position }{position
}
\startarg{MPI{\tt \char`\_}Comm comm }{communicator
}
\par
\subhead{Notes (from the specifications)}
\par
The input value of position is the first location in the output buffer to be
used for packing.  position is incremented by the size of the packed message,
and the output value of position is the first location in the output buffer
following the locations occupied by the packed message.  The comm argument is
the communicator that will be subsequently used for sending the packed
message.
\par
\par
\subhead{Notes for Fortran}
All MPI routines in Fortran (except for {\tt MPI{\tt \char`\_}WTIME} and {\tt MPI{\tt \char`\_}WTICK}) have
an additional argument {\tt ierr} at the end of the argument list.  {\tt ierr
}is an integer and has the same meaning as the return value of the routine
in C.  In Fortran, MPI routines are subroutines, and are invoked with the
{\tt call} statement.
\par
All MPI objects (e.g., {\tt MPI{\tt \char`\_}Datatype}, {\tt MPI{\tt \char`\_}Comm}) are of type {\tt INTEGER
}in Fortran.
\par
\subhead{Errors}
\par
All MPI routines (except {\tt MPI{\tt \char`\_}Wtime} and {\tt MPI{\tt \char`\_}Wtick}) return an error value;
C routines as the value of the function and Fortran routines in the last
argument.  Before the value is returned, the current MPI error handler is
called.  By default, this error handler aborts the MPI job.  The error handler
may be changed with {\tt MPI{\tt \char`\_}Comm{\tt \char`\_}set{\tt \char`\_}errhandler} (for communicators),
{\tt MPI{\tt \char`\_}File{\tt \char`\_}set{\tt \char`\_}errhandler} (for files), and {\tt MPI{\tt \char`\_}Win{\tt \char`\_}set{\tt \char`\_}errhandler} (for
RMA windows).  The MPI-1 routine {\tt MPI{\tt \char`\_}Errhandler{\tt \char`\_}set} may be used but
its use is deprecated.  The predefined error handler
{\tt MPI{\tt \char`\_}ERRORS{\tt \char`\_}RETURN} may be used to cause error values to be returned.
Note that MPI does {\em not} guarentee that an MPI program can continue past
an error; however, MPI implementations will attempt to continue whenever
possible.
\par
\startarg{MPI{\tt \char`\_}SUCCESS }{No error; MPI routine completed successfully.
}
\location{pack.c}
\endmanpage
