\startmanpage
\mantitle{MPI{\tt \char`\_}Cart{\tt \char`\_}create}{tex}{12/9/2006}
\manname{MPI{\tt \char`\_}Cart{\tt \char`\_}create}
--- Makes a new communicator to which topology information has been attached 
\subhead{Synopsis}
\startvb\begin{verbatim}
int MPI_Cart_create(MPI_Comm comm_old, int ndims, int *dims, int *periods, 
                   int reorder, MPI_Comm *comm_cart)

\end{verbatim}
\endvb

\subhead{Input Parameters}
\startarg{comm{\tt \char`\_}old }{input communicator (handle) 
}
\startarg{ndims }{number of dimensions of cartesian grid (integer) 
}
\startarg{dims }{integer array of size ndims specifying the number of processes in 
each dimension 
}
\startarg{periods }{logical array of size ndims specifying whether the grid is 
periodic (true) or not (false) in each dimension 
}
\startarg{reorder }{ranking may be reordered (true) or not (false) (logical) 
}
\par
\subhead{Output Parameter}
\startarg{comm{\tt \char`\_}cart }{communicator with new cartesian topology (handle) 
}
\par
\subhead{Algorithm}
We ignore {\tt reorder} info currently.
\par
\subhead{Thread and Interrupt Safety}
\par
This routine is thread-safe.  This means that this routine may be
safely used by multiple threads without the need for any user-provided
thread locks.  However, the routine is not interrupt safe.  Typically,
this is due to the use of memory allocation routines such as {\tt malloc
}or other non-MPICH runtime routines that are themselves not interrupt-safe.
\par
\subhead{Notes for Fortran}
All MPI routines in Fortran (except for {\tt MPI{\tt \char`\_}WTIME} and {\tt MPI{\tt \char`\_}WTICK}) have
an additional argument {\tt ierr} at the end of the argument list.  {\tt ierr
}is an integer and has the same meaning as the return value of the routine
in C.  In Fortran, MPI routines are subroutines, and are invoked with the
{\tt call} statement.
\par
All MPI objects (e.g., {\tt MPI{\tt \char`\_}Datatype}, {\tt MPI{\tt \char`\_}Comm}) are of type {\tt INTEGER
}in Fortran.
\par
\subhead{Errors}
\par
All MPI routines (except {\tt MPI{\tt \char`\_}Wtime} and {\tt MPI{\tt \char`\_}Wtick}) return an error value;
C routines as the value of the function and Fortran routines in the last
argument.  Before the value is returned, the current MPI error handler is
called.  By default, this error handler aborts the MPI job.  The error handler
may be changed with {\tt MPI{\tt \char`\_}Comm{\tt \char`\_}set{\tt \char`\_}errhandler} (for communicators),
{\tt MPI{\tt \char`\_}File{\tt \char`\_}set{\tt \char`\_}errhandler} (for files), and {\tt MPI{\tt \char`\_}Win{\tt \char`\_}set{\tt \char`\_}errhandler} (for
RMA windows).  The MPI-1 routine {\tt MPI{\tt \char`\_}Errhandler{\tt \char`\_}set} may be used but
its use is deprecated.  The predefined error handler
{\tt MPI{\tt \char`\_}ERRORS{\tt \char`\_}RETURN} may be used to cause error values to be returned.
Note that MPI does {\em not} guarentee that an MPI program can continue past
an error; however, MPI implementations will attempt to continue whenever
possible.
\par
\startarg{MPI{\tt \char`\_}SUCCESS }{No error; MPI routine completed successfully.
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}TOPOLOGY }{Invalid topology.  Either there is no topology 
associated with this communicator, or it is not the correct type (e.g.,
{\tt MPI{\tt \char`\_}CART} when expecting {\tt MPI{\tt \char`\_}GRAPH}).
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}DIMS }{Invalid dimension argument.  A dimension argument
is null or its length is less than or equal to zero.
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}ARG }{Invalid argument.  Some argument is invalid and is not
identified by a specific error class (e.g., {\tt MPI{\tt \char`\_}ERR{\tt \char`\_}RANK}).
}
\location{cart{\tt \char`\_}create.c}
\endmanpage
