\startmanpage
\mantitle{MPI{\tt \char`\_}Graph{\tt \char`\_}neighbors}{tex}{5/8/2006}
\manname{MPI{\tt \char`\_}Graph{\tt \char`\_}neighbors}
--- Returns the neighbors of a node associated  with a graph topology 
\subhead{Synopsis}
\startvb\begin{verbatim}
int MPI_Graph_neighbors(MPI_Comm comm, int rank, int maxneighbors, 
                      int *neighbors)

\end{verbatim}
\endvb

\subhead{Input Parameters}
\startarg{comm }{communicator with graph topology (handle) 
}
\startarg{rank }{rank of process in group of comm (integer) 
}
\startarg{maxneighbors }{size of array neighbors (integer) 
}
\par
\subhead{Output Parameters}
\startarg{neighbors }{ranks of processes that are neighbors to specified process
(array of integer) 
}
\par
\subhead{Thread and Interrupt Safety}
\par
This routine is both thread- and interrupt-safe.
This means that this routine may safely be used by multiple threads and
from within a signal handler.
\par
\subhead{Notes for Fortran}
All MPI routines in Fortran (except for {\tt MPI{\tt \char`\_}WTIME} and {\tt MPI{\tt \char`\_}WTICK}) have
an additional argument {\tt ierr} at the end of the argument list.  {\tt ierr
}is an integer and has the same meaning as the return value of the routine
in C.  In Fortran, MPI routines are subroutines, and are invoked with the
{\tt call} statement.
\par
All MPI objects (e.g., {\tt MPI{\tt \char`\_}Datatype}, {\tt MPI{\tt \char`\_}Comm}) are of type {\tt INTEGER
}in Fortran.
\par
\subhead{Errors}
\par
All MPI routines (except {\tt MPI{\tt \char`\_}Wtime} and {\tt MPI{\tt \char`\_}Wtick}) return an error value;
C routines as the value of the function and Fortran routines in the last
argument.  Before the value is returned, the current MPI error handler is
called.  By default, this error handler aborts the MPI job.  The error handler
may be changed with {\tt MPI{\tt \char`\_}Comm{\tt \char`\_}set{\tt \char`\_}errhandler} (for communicators),
{\tt MPI{\tt \char`\_}File{\tt \char`\_}set{\tt \char`\_}errhandler} (for files), and {\tt MPI{\tt \char`\_}Win{\tt \char`\_}set{\tt \char`\_}errhandler} (for
RMA windows).  The MPI-1 routine {\tt MPI{\tt \char`\_}Errhandler{\tt \char`\_}set} may be used but
its use is deprecated.  The predefined error handler
{\tt MPI{\tt \char`\_}ERRORS{\tt \char`\_}RETURN} may be used to cause error values to be returned.
Note that MPI does {\em not} guarentee that an MPI program can continue past
an error; however, MPI implementations will attempt to continue whenever
possible.
\par
\startarg{MPI{\tt \char`\_}SUCCESS }{No error; MPI routine completed successfully.
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}TOPOLOGY }{Invalid topology.  Either there is no topology 
associated with this communicator, or it is not the correct type (e.g.,
{\tt MPI{\tt \char`\_}CART} when expecting {\tt MPI{\tt \char`\_}GRAPH}).
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}COMM }{Invalid communicator.  A common error is to use a null
communicator in a call (not even allowed in {\tt MPI{\tt \char`\_}Comm{\tt \char`\_}rank}).
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}ARG }{Invalid argument.  Some argument is invalid and is not
identified by a specific error class (e.g., {\tt MPI{\tt \char`\_}ERR{\tt \char`\_}RANK}).
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}RANK }{Invalid source or destination rank.  Ranks must be between
zero and the size of the communicator minus one; ranks in a receive
({\tt MPI{\tt \char`\_}Recv}, {\tt MPI{\tt \char`\_}Irecv}, {\tt MPI{\tt \char`\_}Sendrecv}, etc.) may also be {\tt MPI{\tt \char`\_}ANY{\tt \char`\_}SOURCE}.
}
\location{graph{\tt \char`\_}nbr.c}
\endmanpage
