\startmanpage
\mantitle{MPI{\tt \char`\_}Comm{\tt \char`\_}split}{tex}{12/9/2006}
\manname{MPI{\tt \char`\_}Comm{\tt \char`\_}split}
--- Creates new communicators based on colors and keys 
\subhead{Synopsis}
\startvb\begin{verbatim}
int MPI_Comm_split(MPI_Comm comm, int color, int key, MPI_Comm *newcomm)

\end{verbatim}
\endvb

\subhead{Input Parameters}
\startarg{comm }{communicator (handle) 
}
\startarg{color }{control of subset assignment (nonnegative integer).  Processes 
with the same color are in the same new communicator 
}
\startarg{key }{control of rank assigment (integer)
}
\par
\subhead{Output Parameter}
\startarg{newcomm }{new communicator (handle) 
}
\par
\subhead{Notes}
The {\tt color} must be non-negative or {\tt MPI{\tt \char`\_}UNDEFINED}.
\par
\subhead{Thread and Interrupt Safety}
\par
This routine is thread-safe.  This means that this routine may be
safely used by multiple threads without the need for any user-provided
thread locks.  However, the routine is not interrupt safe.  Typically,
this is due to the use of memory allocation routines such as {\tt malloc
}or other non-MPICH runtime routines that are themselves not interrupt-safe.
\par
\subhead{Notes for Fortran}
All MPI routines in Fortran (except for {\tt MPI{\tt \char`\_}WTIME} and {\tt MPI{\tt \char`\_}WTICK}) have
an additional argument {\tt ierr} at the end of the argument list.  {\tt ierr
}is an integer and has the same meaning as the return value of the routine
in C.  In Fortran, MPI routines are subroutines, and are invoked with the
{\tt call} statement.
\par
All MPI objects (e.g., {\tt MPI{\tt \char`\_}Datatype}, {\tt MPI{\tt \char`\_}Comm}) are of type {\tt INTEGER
}in Fortran.
\par
\subhead{Algorithm}
\begin{verbatim}
  1. Use MPI_Allgather to get the color and key from each process
  2. Count the number of processes with the same color; create a 
     communicator with that many processes.  If this process has
     {\tt MPI_UNDEFINED} as the color, create a process with a single member.
  3. Use key to order the ranks
  4. Set the VCRs using the ordered key values
\end{verbatim}

\par
\subhead{Errors}
\par
All MPI routines (except {\tt MPI{\tt \char`\_}Wtime} and {\tt MPI{\tt \char`\_}Wtick}) return an error value;
C routines as the value of the function and Fortran routines in the last
argument.  Before the value is returned, the current MPI error handler is
called.  By default, this error handler aborts the MPI job.  The error handler
may be changed with {\tt MPI{\tt \char`\_}Comm{\tt \char`\_}set{\tt \char`\_}errhandler} (for communicators),
{\tt MPI{\tt \char`\_}File{\tt \char`\_}set{\tt \char`\_}errhandler} (for files), and {\tt MPI{\tt \char`\_}Win{\tt \char`\_}set{\tt \char`\_}errhandler} (for
RMA windows).  The MPI-1 routine {\tt MPI{\tt \char`\_}Errhandler{\tt \char`\_}set} may be used but
its use is deprecated.  The predefined error handler
{\tt MPI{\tt \char`\_}ERRORS{\tt \char`\_}RETURN} may be used to cause error values to be returned.
Note that MPI does {\em not} guarentee that an MPI program can continue past
an error; however, MPI implementations will attempt to continue whenever
possible.
\par
\startarg{MPI{\tt \char`\_}SUCCESS }{No error; MPI routine completed successfully.
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}COMM }{Invalid communicator.  A common error is to use a null
communicator in a call (not even allowed in {\tt MPI{\tt \char`\_}Comm{\tt \char`\_}rank}).
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}INTERN }{This error is returned when some part of the MPICH 
implementation is unable to acquire memory.  
}
\par
\subhead{See Also}
 MPI{\tt \char`\_}Comm{\tt \char`\_}free
\nextline
\location{comm{\tt \char`\_}split.c}
\endmanpage
