\startmanpage
\mantitle{MPI{\tt \char`\_}Group{\tt \char`\_}range{\tt \char`\_}incl}{tex}{5/8/2006}
\manname{MPI{\tt \char`\_}Group{\tt \char`\_}range{\tt \char`\_}incl}
--- Creates a new group from ranges of ranks in an  existing group 
\subhead{Synopsis}
\startvb\begin{verbatim}
int MPI_Group_range_incl(MPI_Group group, int n, int ranges[][3], 
                         MPI_Group *newgroup)

\end{verbatim}
\endvb

\subhead{Input Parameters}
\startarg{group }{group (handle) 
}
\startarg{n }{number of triplets in array  {\tt ranges} (integer) 
}
\startarg{ranges }{a one-dimensional array of integer triplets, of the 
form (first rank, last rank, stride) indicating ranks in
{\tt group}  or processes to be included in {\tt newgroup}.
}
\par
\subhead{Output Parameter}
\startarg{newgroup }{new group derived from above, in the 
order defined by  {\tt ranges} (handle)
}
\par
\subhead{Thread and Interrupt Safety}
\par
This routine is thread-safe.  This means that this routine may be
safely used by multiple threads without the need for any user-provided
thread locks.  However, the routine is not interrupt safe.  Typically,
this is due to the use of memory allocation routines such as {\tt malloc
}or other non-MPICH runtime routines that are themselves not interrupt-safe.
\par
\subhead{Notes for Fortran}
All MPI routines in Fortran (except for {\tt MPI{\tt \char`\_}WTIME} and {\tt MPI{\tt \char`\_}WTICK}) have
an additional argument {\tt ierr} at the end of the argument list.  {\tt ierr
}is an integer and has the same meaning as the return value of the routine
in C.  In Fortran, MPI routines are subroutines, and are invoked with the
{\tt call} statement.
\par
All MPI objects (e.g., {\tt MPI{\tt \char`\_}Datatype}, {\tt MPI{\tt \char`\_}Comm}) are of type {\tt INTEGER
}in Fortran.
\par
\subhead{Errors}
\par
All MPI routines (except {\tt MPI{\tt \char`\_}Wtime} and {\tt MPI{\tt \char`\_}Wtick}) return an error value;
C routines as the value of the function and Fortran routines in the last
argument.  Before the value is returned, the current MPI error handler is
called.  By default, this error handler aborts the MPI job.  The error handler
may be changed with {\tt MPI{\tt \char`\_}Comm{\tt \char`\_}set{\tt \char`\_}errhandler} (for communicators),
{\tt MPI{\tt \char`\_}File{\tt \char`\_}set{\tt \char`\_}errhandler} (for files), and {\tt MPI{\tt \char`\_}Win{\tt \char`\_}set{\tt \char`\_}errhandler} (for
RMA windows).  The MPI-1 routine {\tt MPI{\tt \char`\_}Errhandler{\tt \char`\_}set} may be used but
its use is deprecated.  The predefined error handler
{\tt MPI{\tt \char`\_}ERRORS{\tt \char`\_}RETURN} may be used to cause error values to be returned.
Note that MPI does {\em not} guarentee that an MPI program can continue past
an error; however, MPI implementations will attempt to continue whenever
possible.
\par
\startarg{MPI{\tt \char`\_}SUCCESS }{No error; MPI routine completed successfully.
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}GROUP }{Null or invalid group passed to function.  
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}INTERN }{This error is returned when some part of the MPICH 
implementation is unable to acquire memory.  
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}ARG }{Invalid argument.  Some argument is invalid and is not
identified by a specific error class (e.g., {\tt MPI{\tt \char`\_}ERR{\tt \char`\_}RANK}).
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}RANK }{Invalid source or destination rank.  Ranks must be between
zero and the size of the communicator minus one; ranks in a receive
({\tt MPI{\tt \char`\_}Recv}, {\tt MPI{\tt \char`\_}Irecv}, {\tt MPI{\tt \char`\_}Sendrecv}, etc.) may also be {\tt MPI{\tt \char`\_}ANY{\tt \char`\_}SOURCE}.
}
\par
\subhead{See Also}
 MPI{\tt \char`\_}Group{\tt \char`\_}free
\nextline
\location{group{\tt \char`\_}range{\tt \char`\_}incl.c}
\endmanpage
