\startmanpage
\mantitle{MPI{\tt \char`\_}Type{\tt \char`\_}create{\tt \char`\_}subarray}{tex}{5/8/2006}
\manname{MPI{\tt \char`\_}Type{\tt \char`\_}create{\tt \char`\_}subarray}
--- Create a datatype for a subarray of a regular,  multidimensional array 
\subhead{Synopsis}
\startvb\begin{verbatim}
int MPI_Type_create_subarray(int ndims,
                           int array_of_sizes[],
                           int array_of_subsizes[],
                           int array_of_starts[],
                           int order,
                           MPI_Datatype oldtype,
                           MPI_Datatype *newtype)

\end{verbatim}
\endvb

\subhead{Input Parameters}
\startarg{ndims }{number of array dimensions (positive integer) 
}
\startarg{array{\tt \char`\_}of{\tt \char`\_}sizes }{number of elements of type oldtype in each dimension of the
full array (array of positive integers) 
}
\startarg{array{\tt \char`\_}of{\tt \char`\_}subsizes }{number of elements of type oldtype in each dimension of
the subarray (array of positive integers) 
}
\startarg{array{\tt \char`\_}of{\tt \char`\_}starts }{starting coordinates of the subarray in each dimension
(array of nonnegative integers) 
}
\startarg{order }{array storage order flag (state) 
}
\startarg{oldtype }{array element datatype (handle) 
}
\par
\subhead{Output Parameter}
\startarg{newtype }{new datatype (handle) 
}
\par
\subhead{Thread and Interrupt Safety}
\par
This routine is thread-safe.  This means that this routine may be
safely used by multiple threads without the need for any user-provided
thread locks.  However, the routine is not interrupt safe.  Typically,
this is due to the use of memory allocation routines such as {\tt malloc
}or other non-MPICH runtime routines that are themselves not interrupt-safe.
\par
\subhead{Notes for Fortran}
All MPI routines in Fortran (except for {\tt MPI{\tt \char`\_}WTIME} and {\tt MPI{\tt \char`\_}WTICK}) have
an additional argument {\tt ierr} at the end of the argument list.  {\tt ierr
}is an integer and has the same meaning as the return value of the routine
in C.  In Fortran, MPI routines are subroutines, and are invoked with the
{\tt call} statement.
\par
All MPI objects (e.g., {\tt MPI{\tt \char`\_}Datatype}, {\tt MPI{\tt \char`\_}Comm}) are of type {\tt INTEGER
}in Fortran.
\par
\subhead{Errors}
\par
All MPI routines (except {\tt MPI{\tt \char`\_}Wtime} and {\tt MPI{\tt \char`\_}Wtick}) return an error value;
C routines as the value of the function and Fortran routines in the last
argument.  Before the value is returned, the current MPI error handler is
called.  By default, this error handler aborts the MPI job.  The error handler
may be changed with {\tt MPI{\tt \char`\_}Comm{\tt \char`\_}set{\tt \char`\_}errhandler} (for communicators),
{\tt MPI{\tt \char`\_}File{\tt \char`\_}set{\tt \char`\_}errhandler} (for files), and {\tt MPI{\tt \char`\_}Win{\tt \char`\_}set{\tt \char`\_}errhandler} (for
RMA windows).  The MPI-1 routine {\tt MPI{\tt \char`\_}Errhandler{\tt \char`\_}set} may be used but
its use is deprecated.  The predefined error handler
{\tt MPI{\tt \char`\_}ERRORS{\tt \char`\_}RETURN} may be used to cause error values to be returned.
Note that MPI does {\em not} guarentee that an MPI program can continue past
an error; however, MPI implementations will attempt to continue whenever
possible.
\par
\startarg{MPI{\tt \char`\_}SUCCESS }{No error; MPI routine completed successfully.
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}TYPE }{Invalid datatype argument.  May be an uncommitted 
MPI{\tt \char`\_}Datatype (see {\tt MPI{\tt \char`\_}Type{\tt \char`\_}commit}).
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}ARG }{Invalid argument.  Some argument is invalid and is not
identified by a specific error class (e.g., {\tt MPI{\tt \char`\_}ERR{\tt \char`\_}RANK}).
}
\location{type{\tt \char`\_}create{\tt \char`\_}subarray.c}
\endmanpage
