\startmanpage
\mantitle{MPI{\tt \char`\_}Get{\tt \char`\_}address}{tex}{12/9/2006}
\manname{MPI{\tt \char`\_}Get{\tt \char`\_}address}
--- Get the address of a location in memory  
\subhead{Synopsis}
\startvb\begin{verbatim}
int MPI_Get_address(void *location, MPI_Aint *address)

\end{verbatim}
\endvb

\subhead{Input Parameter}
\startarg{location }{location in caller memory (choice) 
}
\par
\subhead{Output Parameter}
\startarg{address }{address of location (address) 
}
\par
\subhead{Notes}
This routine is provided for both the Fortran and C programmers.
On many systems, the address returned by this routine will be the same
as produced by the C {\tt \&} operator, but this is not required in C and
may not be true of systems with word- rather than byte-oriented
instructions or systems with segmented address spaces.
\par
This routine should be used instead of {\tt MPI{\tt \char`\_}Address}.
\par
\subhead{Thread and Interrupt Safety}
\par
This routine is both thread- and interrupt-safe.
This means that this routine may safely be used by multiple threads and
from within a signal handler.
\par
\subhead{Notes for Fortran}
All MPI routines in Fortran (except for {\tt MPI{\tt \char`\_}WTIME} and {\tt MPI{\tt \char`\_}WTICK}) have
an additional argument {\tt ierr} at the end of the argument list.  {\tt ierr
}is an integer and has the same meaning as the return value of the routine
in C.  In Fortran, MPI routines are subroutines, and are invoked with the
{\tt call} statement.
\par
All MPI objects (e.g., {\tt MPI{\tt \char`\_}Datatype}, {\tt MPI{\tt \char`\_}Comm}) are of type {\tt INTEGER
}in Fortran.
\par
In Fortran, the integer type is always signed.  This can cause problems
on systems where the address fits into a four byte unsigned integer but
the value is larger than the largest signed integer.  For example, a system
with more than 2 GBytes of memory may have addresses that do not fit within
a four byte signed integer.  Unfortunately, there is no easy solution to
this problem, as there is no Fortran datatype that can be used here (using
a longer integer type will cause other problems, as well as surprising
users when the size of the integer type is larger that the size of a pointer
in C).  In this case, it is recommended that you use C to manipulate
addresses.
\par
\subhead{Errors}
\par
All MPI routines (except {\tt MPI{\tt \char`\_}Wtime} and {\tt MPI{\tt \char`\_}Wtick}) return an error value;
C routines as the value of the function and Fortran routines in the last
argument.  Before the value is returned, the current MPI error handler is
called.  By default, this error handler aborts the MPI job.  The error handler
may be changed with {\tt MPI{\tt \char`\_}Comm{\tt \char`\_}set{\tt \char`\_}errhandler} (for communicators),
{\tt MPI{\tt \char`\_}File{\tt \char`\_}set{\tt \char`\_}errhandler} (for files), and {\tt MPI{\tt \char`\_}Win{\tt \char`\_}set{\tt \char`\_}errhandler} (for
RMA windows).  The MPI-1 routine {\tt MPI{\tt \char`\_}Errhandler{\tt \char`\_}set} may be used but
its use is deprecated.  The predefined error handler
{\tt MPI{\tt \char`\_}ERRORS{\tt \char`\_}RETURN} may be used to cause error values to be returned.
Note that MPI does {\em not} guarentee that an MPI program can continue past
an error; however, MPI implementations will attempt to continue whenever
possible.
\par
\startarg{MPI{\tt \char`\_}SUCCESS }{No error; MPI routine completed successfully.
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}OTHER }{Other error; use {\tt MPI{\tt \char`\_}Error{\tt \char`\_}string} to get more information
about this error code. 
}
\location{get{\tt \char`\_}address.c}
\endmanpage
