\startmanpage
\mantitle{MPI{\tt \char`\_}Win{\tt \char`\_}start}{tex}{5/8/2006}
\manname{MPI{\tt \char`\_}Win{\tt \char`\_}start}
--- Start an RMA access epoch for MPI 
\subhead{Synopsis}
\startvb\begin{verbatim}
int MPI_Win_start(MPI_Group group, int assert, MPI_Win win)

\end{verbatim}
\endvb

\subhead{Input Parameters}
\startarg{group }{group of target processes (handle) 
}
\startarg{assert }{Used to optimize this call; zero may be used as a default.
See notes. (integer) 
}
\startarg{win }{window object (handle) 
}
\par
\subhead{Notes}
The {\tt assert} argument is used to indicate special conditions for the
fence that an implementation may use to optimize the {\tt MPI{\tt \char`\_}Win{\tt \char`\_}start
}operation.  The value zero is always correct.  Other assertion values
may be or'ed together.  Assertions tha are valid for {\tt MPI{\tt \char`\_}Win{\tt \char`\_}start} are:
\par
\startarg{MPI{\tt \char`\_}MODE{\tt \char`\_}NOCHECK }{the matching calls to {\tt MPI{\tt \char`\_}WIN{\tt \char`\_}POST} have already 
completed on all target processes when the call to {\tt MPI{\tt \char`\_}WIN{\tt \char`\_}START} is made. 
The nocheck option can be specified in a start call if and only if it is 
specified in each matching post call. This is similar to the optimization 
of ready-send that may save a handshake when the handshake is implicit in 
the code. (However, ready-send is matched by a regular receive, whereas 
both start and post must specify the nocheck option.) 
}
\par
\subhead{Thread and Interrupt Safety}
\par
This routine is thread-safe.  This means that this routine may be
safely used by multiple threads without the need for any user-provided
thread locks.  However, the routine is not interrupt safe.  Typically,
this is due to the use of memory allocation routines such as {\tt malloc
}or other non-MPICH runtime routines that are themselves not interrupt-safe.
\par
\subhead{Notes for Fortran}
All MPI routines in Fortran (except for {\tt MPI{\tt \char`\_}WTIME} and {\tt MPI{\tt \char`\_}WTICK}) have
an additional argument {\tt ierr} at the end of the argument list.  {\tt ierr
}is an integer and has the same meaning as the return value of the routine
in C.  In Fortran, MPI routines are subroutines, and are invoked with the
{\tt call} statement.
\par
All MPI objects (e.g., {\tt MPI{\tt \char`\_}Datatype}, {\tt MPI{\tt \char`\_}Comm}) are of type {\tt INTEGER
}in Fortran.
\par
\subhead{Errors}
\par
All MPI routines (except {\tt MPI{\tt \char`\_}Wtime} and {\tt MPI{\tt \char`\_}Wtick}) return an error value;
C routines as the value of the function and Fortran routines in the last
argument.  Before the value is returned, the current MPI error handler is
called.  By default, this error handler aborts the MPI job.  The error handler
may be changed with {\tt MPI{\tt \char`\_}Comm{\tt \char`\_}set{\tt \char`\_}errhandler} (for communicators),
{\tt MPI{\tt \char`\_}File{\tt \char`\_}set{\tt \char`\_}errhandler} (for files), and {\tt MPI{\tt \char`\_}Win{\tt \char`\_}set{\tt \char`\_}errhandler} (for
RMA windows).  The MPI-1 routine {\tt MPI{\tt \char`\_}Errhandler{\tt \char`\_}set} may be used but
its use is deprecated.  The predefined error handler
{\tt MPI{\tt \char`\_}ERRORS{\tt \char`\_}RETURN} may be used to cause error values to be returned.
Note that MPI does {\em not} guarentee that an MPI program can continue past
an error; however, MPI implementations will attempt to continue whenever
possible.
\par
\startarg{MPI{\tt \char`\_}SUCCESS }{No error; MPI routine completed successfully.
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}WIN }{Invalid MPI window object
}
\startarg{MPI{\tt \char`\_}ERR{\tt \char`\_}OTHER }{Other error; use {\tt MPI{\tt \char`\_}Error{\tt \char`\_}string} to get more information
about this error code. 
}
\location{win{\tt \char`\_}start.c}
\endmanpage
